### 2024-03-05 presentation/parts/overview_presentation.tex
WIP
Done

    \note[item]{So how does the thesis tackle this problem of building such a system?}
    \note{
        \begin{itemize}
            \item [Chp. 4] Examine how a certain class of generative models can be used to detect data that is different from training data. 
            \item [Chp. 5] Generalize this to be model-agnostic and phrased as a statistical test.
            \item [Chp. 6] Step back and provide an overview of modern methods for unsupervised speech representation learning.
            \item [Chp. 7] Benchmark some of these methods, generative latent variable models, on likelihood and automatic speech recognition.
            \item [Chp. 8] Move to a different domain, medical coding, and provide a critical review of recent works.
            \item [Chp. 9] Provide a retrospective study on a machine learning-assisted stroke recognition system for medical helpline calls.
        \end{itemize}
    }
    \end{frame}

@@

                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1->\tikzoverview
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

>>>>

    \note[item]{So how does the thesis tackle this problem of building such a system?}
    \note{
        \begin{enumerate}
            \item Examine how a certain class of generative models can be used to detect data that is different from training data. 
            \item Generalize this to be model-agnostic and phrased as a statistical test.
            \item Step back and provide an overview of modern methods for unsupervised speech representation learning.
            \item Benchmark some of these methods, generative latent variable models, on likelihood and automatic speech recognition.
            \item Move to a different domain, medical coding, and provide a critical review of recent works.
            \item Provide a retrospective study on a machine learning-assisted stroke recognition system for medical helpline calls.
        \end{enumerate}
    }
\end{frame}

@@

                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1->\tikzoverview
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}

    \note[item]{We want to keep papers that represent each of the three main themes of the thesis: (Uncertainty estimation, representation learning, and clinical applications)}
\end{frame}
